\documentclass{article}
\usepackage{natbib} % To cite


\begin{document}
    \section{General}
    \subsection{Small stuff}
    \begin{itemize}
        \item Put manuscript in PLoS Comp Bio latex template, and also in bioRxiv format? (Cook)$\surd$
        \item Order references chronologically when they appear together. (Smith) $\surd$
        \item Add full stop/coma at the end of every equation (Cook) $\surd$
        \item Make the references to SI consistent with PLoS Comp Bio standards. (Cook) $\surd$
        \item Check that we stay away from the word \textit{taxonomic} along the manuscript we are calling the grouping functional "guilds" now (Lechon)
        \item How do I acknowledge founding? (Pawar) $\surd$
        \item Change in all text "biotically-generated resources" to "leaked resources" and "abiotically-generated resources" to "externally supplied resources" (Clegg, Pawar)
        \item Go through my answers to your comments and check if I addressed them satisfactorily (Pawar)
        \item Revise that legends from figures are still describing things correctly, after the changes we made (all)
        \item Link the model with experiemtally relevant situations. The model is realistic, since it predicts observed patterns (Lechon)
    \end{itemize}
    \subsection{Conceptual stuff}
    \begin{itemize}
        \item Abstract (Lechon)$\surd$
        \item When we are done with this list, proof read of the whole thing to check for typos/grammar/flow... (Lechon, Clegg, Cook, Smith, Pawar)
    \end{itemize}
    \section{Abstract}
    \begin{itemize}
        \item Think of a way of introducing leakage
    \end{itemize}
    \section{Introduction}
    \subsection{Small stuff}
    \begin{itemize}
        \item In line 40, check if the communities in \citep{Lu2018} are indeed \textit{aerobic bacterial communities} (Clegg, Pawar)
    \end{itemize}
    \subsection{Conceptual stuff}
    \begin{itemize}
        \item Think of a way to include leakage in the introduction/discussion without disrupting the reading flow. (Pawaar)
        \item State results at the end of introduction (Smith) $\surd$
    \end{itemize}
    \section{Model}
    \subsection{Conceptual stuff}
    \begin{itemize}
        \item Defend assumptions of the model (Clegg, Pawar, Lechon)
    \end{itemize}
    \section{Competition and Facilitation metrics}
    \subsection{Conceptual stuff}
    \begin{itemize}
        \item Shorten section (Lechon, Pawar) $\surd$
        \item Think of and write an alternative way to present the measures without creating two arbitrary resource categories (Lechon) $\surd$
        \item Check that section is not still too long/detailed (Pawar).
    \end{itemize}
    \section{Simulations}
    \begin{itemize}
        \item Check if the methods are clearly explained (Lechon, Clegg, Cook, Smith, Pawar)
        \item Are the sections on modulating comp-coop still too long? (Pawar)
    \end{itemize}
    \section{Results}
    \subsection{Conceptual stuff}
    \begin{itemize}
        \item Explain the relation between figures 3A and 4A with figure 2 more explicitly (Lechon, Pawar
    \end{itemize}
    \section{Discussion}
    \subsection{Conceptual stuff}
    \begin{itemize}
        \item Should I erase the last sentence of the paper? (Pawar)
        \item Think of whether its worth or not to include a section on stochastic effects in discussion, for example: Finally, stochastic effects were only considered during community assembly, when species were randomly sampled to colonize the initial population. These effects were omitted during community coalescence. Although they have been experimentally shown to be weak \citep{Sierocinki2021}, we cannot ignore that they might had played a significant role in our simulations. (Pawar)
        \item Explain \cite{Yamagishi2020, Yamagishi2020a} a bit more in detail (Smith, Cook) $\surd$
        \item I suspect there is something we can say about the work of \cite{Enke2019, Fant2021, Goldford2018} in relation to our work; particularly supporting the resource class partitioning assumption. Is there? (Clegg, Pawar)
        \item At the end of line 390, I am looking for a reference to back up my \textit{commented} claim about health/climate change/agriculture, if we can't find it, then I will delete that bit, but I think it should be fairly easy to find something (Clegg, Pawar)
    \end{itemize}
    
    \section{Supplementary Material}
    \subsection{Small stuff}
    \begin{itemize}
        \item Replace all synonims with cooperation (Lechon)
    \end{itemize}
    \subsection{Conceptual}
    \begin{itemize}
        \item Clean up (Lechon) $\surd$
        \item merge section 4 with section 3 and shorten $\surd$
        \item Fully derive cumulative demand equation
    \end{itemize}
    \bibliographystyle{agsm}
    \bibliography{references}
\end{document}